Tampering Detection In Low-Power \\ Smart Cameras

### 2015-06-22 paper.tex
Section 4 e Conclusions

%\gi{Adriano: inserisci qui l'algoritmo e traducilo in inglese. Se riusciamo lo spostiamo prima di tutte le sottosezioni}
\vspace{-0.2cm}
\section{Experiments}\label{sec:experiments}
Experiments are meant to assess the advantages of using a segmentation in a tampering-detection framework like Algorithm~\eqref{alg:DISPL}. In particular, to assess the importance of partitioning the scene, we compare Algorithm~\eqref{alg:DISPL} against a solution monitoring the indicators on the whole image (\emph{Total} in Figure~\ref{fig:ROC}). To show that regions have to follow the image content, we consider Algorithm~\eqref{alg:DISPL} when the $K$ regions are obtained by clustering $[r(x), c(x)]$, which yields a Voronoi partitioning of the scene (\emph{Voronoi} in Figure~\ref{fig:ROC}). For both regions defined as in Section~\ref{subsec:Segmentation} and Voronoi regions, we test the two extreme cases where $\Gamma_l = 1$ and $\Gamma_l = K-1$ (respectively, $\Gamma_d = 1$ and $\Gamma_d = K-1$).

\subsubsection{Datasets}
We recorded $8$ sequences from webcams monitoring different urban areas and we synthetically introduced $5\%$ of tampered frames in each. In each sequence we have cropped the central region, removing 50 rows from the top and bottom, and 50 columns from the left and right of the image. Blurring was obtained by convolution against a Gaussian kernel (as in Figure \ref{fig:sequences}(a)), while displacements were simulated by moving the central cropping regions of a random shift between 20 and 50 pixels in each direction (see Figure \ref{fig:sequences}(b)).  Overall, the dataset contains $24410$ frames, in which we inserted $1224$ displacement frames ($5\%$) and $1224$ blurry frames ($5\%$)\footnote{Sequences can be released upon request.}.
\gi{Adriano: image sizes? blur kernel std? quanti pixel il displacement?}
%The second dataset was recorded using a Raspberry Pi Model B+ \cite{raspberry} mounting a camera module.

%Few sequences of the first dataset contain real tampering events  (Figure \ref{fig:indicatori}). 
%In the second dataset, tampering was introduced by moving the device or spraying water on the camera lens. 
\vspace{-0.3cm}
\subsubsection{Performance Assessment}
The typical figure of merit for assessing detection performance in one-shot monitoring methods are the Receiver-Operating Characteristic (ROC) curves: in our case, these can be computed by varying $\gamma_l$, $\gamma_d$ and $\gamma_g$ in a range of values \gi{quale?}. In particular, each point in the ROC curve report a pair of values (1-SPECIFICITY, RECALL) defined as
\[1-\text{SPECIFICITY}_\gamma = \frac{\text{FP}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma}, \ \text{ and } \ \text{RECALL}_\gamma=\frac{\text{TP}_\gamma}{\text{TP}_\gamma+\text{FN}_\gamma}\]
where TP$_\gamma$ represents the number of true positives (tampered frames correctly detected), FP$_\gamma$ of false positives (tampering-free frames detected), TN$_\gamma$ of true negatives (tampering-free frames not detected) and FN$_\gamma$ of false negatives (missed tampered frames), for a given value of $\gamma$.
\vspace{-0.3cm}
\subsubsection{Discussion}
ROC curves in Figure~\ref{fig:ROCdisplacement} and the corresponding values of Area Under the Curve (AUC) reported in the caption, indicate that camera displacements can be effectively detected by all the considered methods, and that Algorithm~\ref{alg:DISPL} achieves the best performance when $\Gamma_l = \Gamma_d = 1$. This result suggests that separately monitoring the luma over image regions is an effective strategy and that the regions have to be suitably estimated.

\emph{We observe that to achieve a recall of $98\%$, Algorithm~\ref{alg:DISPL} operates at $0.3\%$ of false alarms, which is half of the whole image solution ($0.7\%$) and less than one third of the Voronoi solution ($1\%$). Having few false alarms is important in a low-power context, considering the high number of frames that have to be processed. Most importantly, false alerts are halved basically at no computational overhead.} \gi{Aggiornare con i nuovi dati}
In contrast, Figure~\ref{fig:ROC}(c) confirms that when monitoring $g$ it is more convenient to consider the whole scene at once, as typically the regions $\{R_k\}$ do not include the most prominent edge of the scene, which are indeed the most informative part to detect blurring. This is the reason why, in Algorithm~\ref{alg:DISPL}, $g$ is monitored on the whole image.

@@

%Numero di operazioni richieste:
%Calcolo di g(t):
%\begin{itemize}
%\item Norma gradiente: 34 FLOP per pixel
%\item Media delle norme del gradiente
%\end{itemize}
%Calcolo di l(t):
%\begin{itemize}
%\item Media dei valori di grigio
%\item Detrending: 1 FLOP per frame
%\end{itemize}
%Monitoraggio one-shot: 2 confronti
%Monitoraggio sequenziale: 
%Ogni 20 frame
%Calcolo intervalli di confidenza: ~70 FLOP
%Confronto tra intervalli di confidenza: 2 confronti
\vspace{-0.3cm}
\section{Conclusions}\label{sec:Conclusion}
\vspace{-0.1cm}
We presented a tampering detection algorithm that leverages a preliminary image partitioning to improve the detection of camera displacements, and that at the same time can detect blurring. The algorithm has low-computational complexity and is suited for low-power cameras operating at low frame rates.

Ongoing work concern the extension of our solution to other types of tampering, like degradations of the imaging sensor, as well as the integration of this one-shot technique with sequential monitoring scheme such as~\cite{alippi2010detecting}, to leverage the fact that tampering might last more than one frame in the detection. Moreover, we will investigate different segmentation strategies and the application of superpixels methods~\cite{Susstrunk2012} to video sequences by including temporal features in the clustered vectors.

>>>>

%\gi{Adriano: inserisci qui l'algoritmo e traducilo in inglese. Se riusciamo lo spostiamo prima di tutte le sottosezioni}
\vspace{-0.2cm}
\section{Experiments}\label{sec:experiments}
Experiments are meant to assess the advantages of separately monitoring regions in a tampering-detection framework like Algorithm~\ref{alg:DISPL}. To this purpose, we show that Algorithm~\ref{alg:DISPL} outperforms a solution monitoring the indicators on the whole image (\emph{Total} in Figure~\ref{fig:ROC}). We also show that image regions have to be adaptively defined on the image content, and that operating on a Voronoi partition of the scene in $K$ regions obtained by clustering $[r(x), c(x)]$ leads to performance loss (\emph{Voronoi} in Figure~\ref{fig:ROC}). For both regions defined as in Section~\ref{subsec:Segmentation} and Voronoi regions, we test the two extreme cases where $\Gamma_l = 1$ and $\Gamma_l = K-1$ (respectively, $\Gamma_d = 1$ and $\Gamma_d = K-1$).

We recorded $8$ sequences from webcams monitoring different urban areas, yielding overall $24410$ frames. From each frame we have cropped the central area, removing the 50 top-most and bottom-most rows, and the 50 left-most and right-most columns. We have synthetically introduced $5\%$ of tampered frames: displacements have been simulated by moving the central cropping area of a random shift having magnitude between 20 and 50 rows and coulumns (as in Figure \ref{fig:sequences}(b)). Blurring was simulated by convolution against a Gaussian kernel (as in Figure \ref{fig:sequences}(a)). \footnote{Sequences can be released upon request.}.
\gi{Adriano: image sizes? blur kernel std? quanti pixel il displacement?}

%The second dataset was recorded using a Raspberry Pi Model B+ \cite{raspberry} mounting a camera module. 
%Few sequences of the first dataset contain real tampering events  (Figure \ref{fig:indicatori}). 
%In the second dataset, tampering was introduced by moving the device or spraying water on the camera lens.

The typical figure of merit for assessing detection performance in one-shot monitoring methods are the Receiver-Operating Characteristic (ROC) curves: in our case, these can be computed by varying $\gamma_l$, $\gamma_d$ and $\gamma_g$ in a range of values \gi{quale?}. In particular, each point in the ROC curve report a pair of values (1-SPECIFICITY$_\gamma$, RECALL$_\gamma$) defined as
\[1-\text{SPECIFICITY}_\gamma = \frac{\text{FP}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma}, \ \text{ and } \ \text{RECALL}_\gamma=\frac{\text{TP}_\gamma}{\text{TP}_\gamma+\text{FN}_\gamma}\]
where TP$_\gamma$ represents the number of true positives (tampered frames correctly detected), FP$_\gamma$ of false positives (tampering-free frames detected), TN$_\gamma$ of true negatives (tampering-free frames not detected) and FN$_\gamma$ of false negatives (missed tampered frames), for a given value of $\gamma$.
\vspace{-0.3cm}
\subsubsection{Discussion}
ROC curves in Figure~\ref{fig:ROC}(a)-(b) and the Area Under the Curve (AUC) values reported in the caption indicate that camera displacements can be effectively detected by all the considered methods; the comparison against Voronoi regions suggests that a more substantial advantage is guaranteed when regions fit the scene content. As far as the values of $\Gamma_l$ and $\Gamma_d $ are concerned, the best option is to raise an alert as soon as a single region provides a very clear outlier (i.e., interval \eqref{eq:confidenceRegions} are quite wide). This option is preferable with respect to requiring $K-1$ regions to simultaneously fire an outlier, because it also enable the detection of partial occlusions of the scene. Overall, the ROC curves confirm that $d$ is a far more effective indicator than $l$ in detecting camera displacements.

\emph{We observe that to achieve a recall of $98\%$, Algorithm~\ref{alg:DISPL} operates at $0.3\%$ of false alarms, which is half of the whole image solution ($0.7\%$) and less than one third of the Voronoi solution ($1\%$). Having few false alarms is important in a low-power context, considering the high number of frames that have to be processed. Most importantly, false alerts are halved basically at no computational overhead.} \gi{Aggiornare con i nuovi dati}

In contrast, Figure~\ref{fig:ROC}(c) confirms that blurring are more effectively detected by monitoring the whole scene at once. This is probably due to the fact that typically, regions $\{R_k\}$ do not include the most prominent edge of the scene, which are indeed the most informative part to detect blurring. This is the reason why, in Algorithm~\ref{alg:DISPL}, $g$ is monitored on the whole image.\gi{aggiungere commento su K-1 vornoi che va meglio?}

@@

%Numero di operazioni richieste:
%Calcolo di g(t):
%\begin{itemize}
%\item Norma gradiente: 34 FLOP per pixel
%\item Media delle norme del gradiente
%\end{itemize}
%Calcolo di l(t):
%\begin{itemize}
%\item Media dei valori di grigio
%\item Detrending: 1 FLOP per frame
%\end{itemize}
%Monitoraggio one-shot: 2 confronti
%Monitoraggio sequenziale: 
%Ogni 20 frame
%Calcolo intervalli di confidenza: ~70 FLOP
%Confronto tra intervalli di confidenza: 2 confronti
\vspace{-0.3cm}
\section{Conclusions}\label{sec:Conclusion}
\vspace{-0.1cm}
We presented a tampering-detection algorithm that leverages an image segmentation to improve the detection of camera displacements, and that at the same time can detect blurring. The algorithm has low-computational complexity and has to be considered a prompt trigger for detecting tampering in low-power and ultra low-power cameras operating at low frame rates.

Ongoing work concerns investigations towards other types of tampering, like degradations of the imaging sensor, as well as the integration of sequential monitoring schemes~\cite{alippi2010detecting} to detect subtle tampering that persists over time. Moreover, we will investigate the use of superpixels methods~\cite{Susstrunk2012} to perform the preliminary scene segmentation, by including suitable temporal information to the feature vectors.
